### 2020-09-17 paper/Credit_Author_Statement/Credit_Author_Statement.tex

\begin{document}
\begin{frontmatter}
\title{Preliminary design of control rods in the single-fluid double-zone thorium molten salt reactor (SD-TMSR)}
\end{frontmatter}
\section*{Highlights}
\begin{itemize}
	\item A reliable safety system based on control rods has been introduced in the SD-TMSR.
	\item Three different initial fissile loadings are considered.
	\item Six different absorbing materials have been investigated.
	\item Integral and differential control rod worth, SDM, and shadowing effects at steady-state were calculated.
	\item SERPENT-2 Monte-Carlo code was used to calculate the reactivity worth.
\end{itemize}
\end{document}

>>>>

\begin{document}
\begin{frontmatter}
\title{Credit Author Statement}
\end{frontmatter}
\section*{The authors contributed to this work as described below}
\begin{itemize}
	\item \textbf{Osama Ashraf} conceived and designed the simulations, wrote the paper, prepared figures 
	and/or tables, performed the computation work, and reviewed drafts of the paper.
	\item \textbf{Andrei Rykhlevskii} conceived and designed the simulations, wrote the paper, prepared figures 
	and/or tables, performed the computation work, and reviewed drafts of the paper.
	\item \textbf{G. V. Tikhomirov} directed and supervised the work, conceived and designed the simulations and reviewed drafts of the paper.
	\item \textbf{Kathryn D. Huff} supervised the work, conceived and contributed to conception of the simulations, and reviewed drafts of the paper.
\end{itemize}
\end{document}

### 2020-09-17 paper/cover-letter/cover-letter.tex
Before submitting to Annals

\documentclass[11pt]{letter} % Default font size of the document, change to 10pt to fit more text
\usepackage{graphicx}
%\usepackage{newcent} % Default font is the New Century Schoolbook PostScript font
%\usepackage{helvet} % Uncomment this (while commenting the above line) to use the Helvetica font

@@

		Please find enclosed a manuscript entitled: ``Preliminary design of control rods in the single-fluid double-zone thorium molten salt reactor (SD-TMSR)'' which I and my coauthors (Mr. Andrei Rykhlevskii, Prof. G. V. Tikhomirov, and Prof. Kathryn D. Huff) are submitting for exclusive consideration of publication as a research article in Annals of Nuclear Energy. The current manuscript introduces a reliable safety system based on control rods in addition to the online feed system reactivity control in the SD-TMSR. This paper focuses on control rod design and material selection, integral and differential control rod worth, shutdown margin, and shadowing effects at steady state.

		Notably, this paper in its initial form has been rejected from Progress of Nuclear Energy journal. However, we have addressed the major concerns of the reviewers. It is our belief that the manuscript is substantially improved after implementing the suggested comments and edits.

		In the present paper, all calculations presented were performed using Monte-Carlo code SERPENT-2. We considered three different initial fissile loadings and applied six different absorbing materials to investigate the main operational and safety parameters in the SD-TMSR. Result showed that $^{233}$U and reactor-grade Pu startup cores maintain adequate shutdown margin with all considered absorbers. Finally, this paper proposes a design of control rod clusters that compensate the excess reactivity of the SD-TMSR loaded with different initial fissile material.

		Thank you for your consideration of our work. We expect it will be of interest
		to a broad readership concerned with simulation of MSRs.\\

>>>>

\documentclass[10.5pt]{letter} % Default font size of the document, change to 10pt to fit more text
\usepackage{graphicx}
%\usepackage{newcent} % Default font is the New Century Schoolbook PostScript font
%\usepackage{helvet} % Uncomment this (while commenting the above line) to use the Helvetica font

@@

		Please consider our revised manuscript, ``Preliminary design of control rods in the single-fluid double-zone thorium molten salt reactor (SD-TMSR)'' which I and my coauthors (Dr. Andrei Rykhlevskii, Prof. G. V. Tikhomirov, and Prof. Kathryn D. Huff) are submitting for publication as a research article 
		in Annals of Nuclear Energy.

		We appreciate the interest that the editors and reviewers have taken in our manuscript and the constructive suggestions they have given. We have addressed the major concerns of the reviewers. It is our belief that the manuscript is substantially improved after making the suggested edits.

		Following this letter is the detailed response to reviewers. We included the 
		answers in the manuscript. Changes made in the manuscript are marked using track changes.

	Thank you again for consideration of our revised manuscript.

### 2020-09-17 paper/introduction.tex

The online reprocessing and refueling system is designed to operate as a long-term reactivity control in the MSRs \cite{ashraf2019modeling,ashraf2019Preliminary}. However, we cannot rely on online reprocessing to adjust reactivity quickly, because loop time (time needed for one particle to make one full circulation through the primary loop) is approximately 20 seconds for MSBR and its analogs. Consequently, we need a prompt reactivity control system for emergencies. The most common and reliable way to control the reactivity is to insert or withdraw control rods made of a material with a large neutron absorption cross section (e.g., boron).
Insertion of control rods introduces negative reactivity into the 
core which helps to compensate the excess reactivity and 
adjust the power level of the core or shut down the reactor in case of 
emergency. Therefore, we should estimate 
the reactivity worth of the control rods.
The reactivity worth of control rods correlates with the interference 
(shadowing effects) between control rod clusters 
\cite{vcerba2017optimization}. 
The control rod worth and its efficiency in compensating excess reactivity is a subject of significant interest since it directly affects reactor safety \cite{atkinson2019small}. Additionally, the Nuclear Regulatory Commission (NRC) prescribes that one of two independent reactivity control systems should use control rods (Criterion 26) \cite{nuclear1987standard}.

>>>>

The online reprocessing and refueling system is designed to operate as a long-term reactivity control in the MSRs \cite{ashraf2019modeling,ashraf2019Preliminary}. However, we cannot rely on online reprocessing to adjust reactivity quickly, because loop time (time needed for one particle to make one full circulation through the primary loop) is approximately 20 seconds for MSBR and its analogs. Consequently, we need a prompt reactivity control system for emergencies. The most common and reliable way to control the reactivity is to insert or withdraw control rods made of a material with a large neutron absorption cross section (e.g., boron).
Insertion of control rods introduces negative reactivity into the 
core which helps to compensate the excess reactivity and 
adjust the power level of the core or shut down the reactor in case of 
emergency. Therefore, we should estimate 
the reactivity worth of the control rods.
The reactivity worth of control rods correlates with the interference 
(shadowing effects) between control rod clusters 
\cite{vcerba2017optimization}. 
The control rod worth and its efficiency in compensating excess reactivity is a subject of significant interest since it directly affects the reactor safety \cite{atkinson2019small}. Additionally, the Nuclear Regulatory Commission (NRC) prescribes that one of two independent reactivity control systems should use control rods (Criterion 26) \cite{nuclear1987standard}. According to the demands of nuclear safety regulations, two independent shutdown systems must be adopted in reactor design to ensure the reactor safe operation, to adjust power, and to ensure the shutdown of the reactor anytime independently. All the shutdown systems must be sufficient to shut down the reactor at any time during operation.
